Unity in diversity: shared basic social-cognitive processing in children from from 17 diverse communities

### 2024-01-31 paper/supplement.Rmd
update supllement

```{r}
data <- read_csv("../data/gafo-cc-clean-data.csv")%>%
  mutate(continent = ifelse(
    community %in% c("leipzig", "plymouth"), "Europe", 
    ifelse(
      community %in% c("akure", "hai||om", "khwe", "chimfunshi", "bandongo", "bayaka", "windhoek", "uganda"), "Africa",
      ifelse(community %in% c("stanford", "mexico", "buenos_aires"), "America",
             ifelse(community %in% c("india", "beijing", "turkey"), "Asia", "Oceania"))
    )
  ))%>%
  mutate(continent = factor(continent, levels = c("America", "Africa", "Europe", "Asia", "Oceania"), ordered = T))%>%
  mutate(community = recode(community,
                            akure = "Akure (Nigeria)",
                            leipzig = "Leipzig (Germany)",
                            `hai||om` = "Hai||om (Namibia)",
                            khwe = "Khwe (Namibia)",
                            windhoek = "Windhoek (Namibia)",
                            stanford = "Stanford (USA)",
                            chimfunshi = "Chimfunshi (Sambia)",
                            mexico = "Ocuilan (Mexico)",
                            plymouth = "Plymouth (UK)",
                            beijing = "Beijing (China)", 
                            india = "Pune (India)",
                            buenos_aires = "Buenos Aires (Argentina)",
                            auckland = "Auckland (New Zealand)",
                            turkey = "Malatya (Turkey)",
                            bandongo = "Bandongo (Rep. Congo)",
                            bayaka = "BaYaka (Rep. Congo)", 
                            uganda = "Nyabyeya (Uganda)"))
```

@@

A total of `r sum(as.numeric(demtab$N))` children between `r round(min(data$ageinyears), 2)` and `r round(max(data$ageinyears), 2)` provided data for the study. Children lived in `r n_distinct(data$community)` different communities, located in `r n_distinct(data$country)` different countries. Table \@ref(tab:demtable) gives the sample size per community together with some basic demographic information. Figure \@ref(fig:figpred1)A shows the age distribution in each setting. Additional children were recruited but did not contribute data to the study. The recruitment strategy varied from community to community and we therefore cannot provide detailed information about the number of children that were excluded. All children who contributed at least four valid data points were included in the final sample. We did not exclude any participants for performance reasons. A detailed description of each site and the way children were recruited can be found below.

@@

# dempred <- data%>%
#   group_by(community,continent)%>%
#   mutate(older_children = children - 1 - younger_children)%>%
#   distinct(subjid, .keep_all = T)%>%
#   select(subjid, community, continent, older_children,children, younger_children, household)%>%
#   pivot_longer(names_to = "dem", values_to = "value", cols = c(older_children,children, younger_children, household))%>%
#   mutate(dem = recode(dem,
#                       older_children = "older children",
#                             younger_children = "younger children"),
#          dem = factor(dem, levels = c("household", "children", "older children", "younger children")))%>%
#   ggplot(aes(y = community, x = value))+
#   facet_grid(continent~dem, scales = "free", space = "free_y")+
#   geom_density_ridges(
#     jittered_points = TRUE,
#     position = position_points_jitter(width = 0.25, height = 0),
#     point_shape = '|',  point_alpha = 1, alpha = 0.7,
#   )+
#  # geom_density_ridges(
#  #    col = "white",
#  #    jittered_points = TRUE, quantile_lines = TRUE, scale = 0.9, alpha = 0.7,
#  #    vline_size = 1, vline_color = "red",
#  #    point_size = 0.4, point_alpha = 1,
#  #    position = position_raincloud(adjust_vlines = TRUE)
#  #  )
#   labs(x = "No. of individuals", y= "")+
#   #geom_jitter(alpha = .1, width = 0.1, height = 0.1)+
#   theme_few()
# 
# ggsave(plot = dempred, "../visuals/dempred.png", height = 8, width = 14, scale = 1.1)

@@

```{r}
mdata <- data%>%
  ungroup()%>%
  mutate(older_children = children - 1 - younger_children)%>%
  mutate(ageinyears = scale(ageinyears),
         targetcentralityx = scale(targetcentralityx),
         trialnr = scale(trialnr),
         touchscreen = factor(touchscreen),
         screen = factor(screen),
         click = abs(clickdistfromtargetcenterx))
```

```{r}
bm_null <- brm(click ~ ageinyears + targetcentralityx + (trialnr + targetcentralityx|subjid),
                              data   = mdata,
                              family = lognormal(),
                              warmup = 2000,
                              iter   = 6000,
                              chains = 4,
                              cores  = 4,
                              threads = threading(8),
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")

saveRDS(bm_null, "../saves/bm_cv_null.rds")

bm_cult <- brm(click ~ ageinyears + targetcentralityx + (trialnr + targetcentralityx|subjid)+ (1 |community),
                              data   = mdata,
                              family = lognormal(),
                              warmup = 2000,
                              iter   = 6000,
                              chains = 4,
                              cores  = 4,
                              threads = threading(8),
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")

saveRDS(bm_cult, "../saves/bm_cv_cult.rds")

bm_cult_age <- brm(click ~ ageinyears + targetcentralityx + (trialnr + targetcentralityx|subjid)+ (ageinyears + targetcentralityx |community),
                              data   = mdata,
                              family = lognormal(),
                              warmup = 2000,
                              iter   = 6000,
                              chains = 4,
                              cores  = 4,
                              threads = threading(8),
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")

saveRDS(bm_cult_age, "../saves/bm_cv_cult_age.rds")

fixef(bm_cult_age)%>%as_tibble(rownames = "term")%>%mutate_if(is.numeric, round, 2)%>%saveRDS(.,"../saves/cult_age_fix.rds")

@@

```{r}
six_fold_cross_validation <- function(data, m1, m2, m3, m4, repeats) {

  N_ids = n_distinct(data$subjid)
#Prepare results DF
  results <- tibble(
    m1_score=numeric(), 
    m2_score=numeric(), 
    m3_score=numeric(), 
    #m4_score=numeric(),

    #m4_beats_m3=logical(), 
    #m4_beats_m2=logical(), 
    #m4_beats_m1=logical(), 
    m3_beats_m2=logical(), 
    m3_beats_m1=logical(), 
    m2_beats_m1=logical(),

    m1 = character(), 
    m2 = character(), 
    m3 = character(),
    #m4 = character()
    )

#Repeat the whole shebang several times
  for(i in 1:repeats) {

  # Split dataset into 6 bins
  bin_data <- data%>%distinct(community, subjid)%>%group_by(community) %>% mutate(bin = rep(1:6, length.out = n()))

for(j in 1:6) {
    # Use bin j as "hold out" data
    testing_ids <- bin_data%>%filter(bin == j)%>%pull(subjid)
    training_ids <- bin_data%>%filter(bin != j)%>%pull(subjid)
    # Safety check - is partition complete and disjoint?
    stopifnot(length(testing_ids) + length(training_ids) == N_ids)
    stopifnot(length(intersect(testing_ids, training_ids)) == 0)
# Create two separate dataframes
    testing_data <- filter(data, subjid %in% testing_ids)
    training_data <- filter(data, subjid %in% training_ids)

    # Train models
    up_m1 <- update(m1, newdata=training_data, cores=4,backend = "cmdstanr", threads = threading(8))
    up_m2 <- update(m2, newdata=training_data, cores=4,backend = "cmdstanr", threads = threading(8))
    up_m3 <- update(m3, newdata=training_data, cores=4,backend = "cmdstanr", threads = threading(8))
    #up_m4 <- update(m4, newdata=training_data, cores=4,backend = "cmdstanr", threads = threading(8))

    # Sample predictions
    preds_m1 <- posterior_predict(up_m1, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")
    preds_m2 <- posterior_predict(up_m2, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")
    preds_m3 <- posterior_predict(up_m3, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")
    #preds_m4 <- posterior_predict(up_m4, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")

    # Evaluate predictive accuracy
  score_m1 <- mean(sqrt(colMeans((testing_data$click - t(preds_m1))**2)))
  score_m2 <- mean(sqrt(colMeans((testing_data$click - t(preds_m2))**2)))
  score_m3 <- mean(sqrt(colMeans((testing_data$click - t(preds_m3))**2)))
  #score_m4 <- mean(sqrt(colMeans((testing_data$click - t(preds_m4))**2)))

  m1_name <-  as.character(substitute(m1))
  m2_name <-  as.character(substitute(m2))
  m3_name <-  as.character(substitute(m3))
  #m4_name <-  as.character(substitute(m4))

    # Record results
    results <- add_row(results,

                       repeats = i, 
                       bin = j,

                       m1_score = score_m1,
                       m2_score = score_m2,
                       m3_score = score_m3,
                       #m4_score = score_m4,

                       # m4_beats_m3 = m4_score < m3_score,
                       # m4_beats_m2 = m4_score < m2_score,
                       # m4_beats_m2 = m4_score < m1_score,
                       m3_beats_m2 = m3_score < m2_score,
                       m3_beats_m1 = m3_score < m1_score,
                       m2_beats_m1 = m2_score < m1_score,

                       m1  = m1_name,
                       m2 = m2_name,
                       m3 = m3_name,
                       #m4 = m4_name
                       )
 }
  }
  return(results)
}
```

```{r}
cv_cult <- six_fold_cross_validation(scdata, bm_base, bm_cult, bm_cult_age, 1)
```

@@

This prediction is best understood by considering a similar phenomenon: pointing a torch light to a flat surface. The width of the light beam represents each individual's level of uncertainty in vector estimation and is represented in the model as a normal distribution around the true gaze vector with a participant specific standard deviation. On each trial, the model assumes that the participant samples a vector from this distribution to infer the location of the balloon. The smaller the standard deviation -- -- the narrower the light beam --, the more precise on average the participant is. Now, when the torch is directed straight down, the light beam is concentrated in a relatively small area. When the torch is rotated to the side, the the light from one half of the cone must travel further than the light from the other half to reach the surface. As a consequence, the light is spread over a wider area. This is true no matter how wide the cone (how large the standard deviation) is.

```{r}
draws <- bind_rows(
as_draws_df(bm_cult_age)%>%
  select(contains("ageinyears"))%>%
  select(contains("ageinyears"))%>%
  select(-contains("sd"))%>%
  select(-contains("cor"))%>%
  pivot_longer(cols = contains("ageinyears]"), names_to = "community", values_to = "value")%>%
  mutate(post = value + b_ageinyears,
         community = str_remove(community, "r_community"),
         community = str_remove(community, ",ageinyears]"),
         community = str_remove(community, "\\["))%>%
  select(community, post)%>%
  mutate(type = "ageinyears"),

as_draws_df(bm_cult_age)%>%
  select(contains("targetcentralityx"))%>%
  select(contains("targetcentralityx"))%>%
  select(-contains("sd"))%>%
  select(-contains("cor"))%>%
  select(-contains("subjid"))%>%
  pivot_longer(cols = contains("targetcentralityx]"), names_to = "community", values_to = "value")%>%
  mutate(post = value + b_targetcentralityx,
         community = str_remove(community, "r_community"),
         community = str_remove(community, ",targetcentralityx]"),
         community = str_remove(community, "\\["))%>%
  select(community, post)%>%
  mutate(type = "targetcentrality")
)%>%
  mutate(community = str_replace(community, "\\.", " "),
         community= str_remove(site,"\\."))

pdraws <- draws%>%
  mutate(community = recode(community, 
                            "Auckland (NewZealand)" = "Auckland (New Zealand)",
                            "BaYaka (Rep.Congo)" = "BaYaka (Rep. Congo)",
                            "Bandongo (Rep.Congo)" = "Bandongo (Rep. Congo)",
                            "Buenos Aires(Argentina)" = "Buenos Aires (Argentina)"))%>%
  left_join(data%>%distinct(community, continent))%>%
  mutate(continent = factor(continent, levels = c("America", "Africa", "Europe", "Asia", "Oceania"), ordered = T))

saveRDS(pdraws, "../saves/pdraws.rds")

post_agg <- pdraws%>%
  group_by(community, type)%>%
  summarise(mean = mean(post),
            lci = hdi_lower(post),
            uci = hdi_upper(post))

saveRDS(post_agg, "../saves/post_agg.rds")
```

@@

To test these predictions, we inspected the parameter estimates for age and target centrality in the "winning" `culture_age` model described in the previous sections. We found strong main effects of age ($\beta$ = ) and target centrality ($\beta$ =). Figure \@ref(fig:figpreds) visualizes the posterior distributions for each cultural setting and shows that -- despite variation in strength -- there was a strong effect of age and target centrality in all cultural settings.

Another way to look at these signatures is to visualize the group-level developmental trajectories and the aggregated performance at different areas of the screen. Figure \@ref(fig:figdev)A shows that children got more precise with age in all cultural settings. Figure \@ref(fig:figdev)B shows the expected u-shaped pattern: the closer the balloon lands to the center of the screen (bins 5 and 6) the more precise children are in all cultural settings.

@@

```{r}
am <- ggplot()+
  geom_point(data = mdata%>%filter(continent == "America"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
  geom_smooth(data = post%>%filter(continent == "America"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
  theme_few()+
  scale_fill_colorblind(name = "")+
  scale_color_colorblind(name = "")+
  labs(x = "", y="Imprecision")+
  scale_x_continuous(limits = c(2,10))+
  scale_y_continuous(limits = c(0,1000))+
  facet_grid(continent~.)+
  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))

af <- ggplot()+
  geom_point(data = mdata%>%filter(continent == "Africa"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
  geom_smooth(data = post%>%filter(continent == "Africa"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
  theme_few()+
  scale_fill_colorblind(name = "")+
  scale_color_colorblind(name = "")+
  labs(x = "", y="")+
    scale_x_continuous(limits = c(2,10))+
  scale_y_continuous(limits = c(0,1000))+
  facet_grid(continent~.)+
  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))

eu <- ggplot()+
  geom_point(data = mdata%>%filter(continent == "Europe"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
  geom_smooth(data = post%>%filter(continent == "Europe"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
  theme_few()+
  scale_fill_colorblind(name = "")+
  scale_color_colorblind(name = "")+
  labs(x = "", y="")+
    scale_x_continuous(limits = c(2,10))+
  scale_y_continuous(limits = c(0,1000))+
  facet_grid(continent~.)+
  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))

as <- ggplot()+
  geom_point(data = mdata%>%filter(continent == "Asia"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
  geom_smooth(data = post%>%filter(continent == "Asia"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
  theme_few()+
  scale_fill_colorblind(name = "")+
  scale_color_colorblind(name = "")+
  labs(x = "", y="")+
    scale_x_continuous(limits = c(2,10))+
  scale_y_continuous(limits = c(0,1000))+
  facet_grid(continent~.)+
  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))

oc <- ggplot()+
  geom_point(data = mdata%>%filter(continent == "Oceania"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
  geom_smooth(data = post%>%filter(continent == "Oceania"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
  theme_few()+
  scale_fill_colorblind(name = "")+
  scale_color_colorblind(name = "")+
  labs(x = "Age", y="")+
    scale_x_continuous(limits = c(2,10))+
  scale_y_continuous(limits = c(0,1000))+
  facet_grid(continent~.)+
  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
```

@@

Table \@ref(tab:bftable) shows the Bayes Factors in favor of the vector-based gaze estimation model for each cultural setting. The evidence in favor of the gaze model compared to the two alternative models was clear (all BF > 1 000 000 000 000 000). This result clearly rules out that the u-shaped pattern in the data was the result of participants always clicking the center instead of following gaze.

```{r bftable, echo=F}
bf <- readRDS("../model/output/bf_comparison.rds")%>%
  mutate_if(is.numeric, format, digits = 2, nsmall = 2)

@@

We asked about children's exposure to screens as well as touchscreens. These two variables were largely redundant (see Figure Figure \@ref(fig:figpred1)B) and so we included only one of them in the model. We chose the availability of a touchscreen as a predictor because the task itself was presented on a touchscreen. We expected (and pre-registered) that children with exposure to touchscreens would perform better.

For household composition, we asked for the total number of people in the household, the number of children and the number of younger children. Based on this, we also computed the number of older children living in the household. We did not pre-register this, but decided to also include this variable because prior work on advanced forms of social cognition has suggested that the presence of older siblings is slightly more predictive of development compared to other aspects of household composition [e.g., @lewis1996social; @ruffman1998older; but see @peterson2003opening]. We think that gaze following improves though practice during social interaction. Particularly supportive, we believe, are situations in which it is difficult to infer the goals and intentions of another person based on other information sources (e.g., language or context). In such situations, children have to pay closer attention to the interaction partner and use their gaze to make such inferences. We are well aware that the numbers in the questionnaire are very far removed from these forms of social interaction. Thus, at best, they are a very coarse approximation. As a consequence, we do not expect there to be a very strong link between the two. We sincerely hope that future work will be able to directly assess children's social interactions. We standardized each predictor *within* each culture before fitting the models. Thus, the interpretation of the coefficient is the gain in precision for living e.g., in a larger household relative to other children from the same cultural settings.

@@

ggsave(plot = pcomtc, "../visuals/pcomtc.png", height = 4, width = 5, scale = 1.5)
```

>>>>

```{r}
data <- read_csv("../data/gafo-cc-clean-data.csv")%>%
  mutate(continent = ifelse(
    community %in% c("leipzig", "plymouth"), "Europe", 
    ifelse(
      community %in% c("akure", "hai||om", "khwe", "chimfunshi", "bandongo", "bayaka", "windhoek", "uganda"), "Africa",
      ifelse(community %in% c("stanford", "mexico", "buenos_aires"), "America",
             ifelse(community %in% c("india", "beijing", "turkey"), "Asia", "Oceania"))
    )
  ))%>%
  mutate(continent = factor(continent, levels = c("America", "Africa", "Europe", "Asia", "Oceania"), ordered = T))%>%
  mutate(community = recode(community,
                            akure = "Akure (Nigeria)",
                            leipzig = "Leipzig (Germany)",
                            `hai||om` = "Hai||om (Namibia)",
                            khwe = "Khwe (Namibia)",
                            windhoek = "Windhoek (Namibia)",
                            stanford = "Stanford (USA)",
                            chimfunshi = "Chimfunshi (Zambia)",
                            mexico = "Ocuilan (Mexico)",
                            plymouth = "Plymouth (UK)",
                            beijing = "Beijing (China)", 
                            india = "Pune (India)",
                            buenos_aires = "Buenos Aires (Argentina)",
                            auckland = "Auckland (New Zealand)",
                            turkey = "Malatya (Türkiye)",
                            bandongo = "Bandongo (Rep. Congo)",
                            bayaka = "BaYaka (Rep. Congo)", 
                            uganda = "Nyabyeya (Uganda)"))
```

@@

A total of `r sum(as.numeric(demtab$N))` children between `r round(min(data$ageinyears), 2)` and `r round(max(data$ageinyears), 2)` provided data for the study. Children lived in `r n_distinct(data$community)` different communities, located in `r n_distinct(data$country)` different countries. Table \@ref(tab:demtable) gives the sample size per community together with some basic demographic information. Figure \@ref(fig:figpred1)A shows the age distribution in each setting. For some children, the exact birthday was unknown. In such cases, we set the birthday to the 30th of June of the year that would make them fall into the reported age category. Additional children were recruited but did not contribute data to the study. The recruitment strategy varied from community to community and we therefore cannot provide detailed information about the number of children that were excluded. All children who contributed at least four valid data points were included in the final sample, however, we excluded children when parents did not fill out the questionnaire correctly (e.g., when the number of children living in the household was reported to be larger than the household itself or when the number of children reported to live in the household equaled the number of children younger than the child being tested). Twelve children had to be excluded for one of these reasons (one from Akure, two from Stanford, seven from Pune and two from Windhoek). We did not exclude any participants for performance reasons. A detailed description of each site and the way children were recruited can be found below.

@@

dempred <- data%>%
  group_by(community,continent)%>%
  mutate(older_children = children - 1 - younger_children)%>%
  distinct(subjid, .keep_all = T)%>%
  select(subjid, community, continent, older_children,children, younger_children, household)%>%
  pivot_longer(names_to = "dem", values_to = "value", cols = c(older_children,children, younger_children, household))%>%
  mutate(dem = recode(dem,
                      older_children = "older children",
                            younger_children = "younger children"),
         dem = factor(dem, levels = c("household", "children", "older children", "younger children")))%>%
  ggplot(aes(y = community, x = value))+
  facet_grid(continent~dem, scales = "free", space = "free_y")+
  geom_density_ridges(
    jittered_points = TRUE,
    position = position_points_jitter(width = 0.25, height = 0),
    point_shape = '|',  point_alpha = 1, alpha = 0.7,
  )+
 # geom_density_ridges(
 #    col = "white",
 #    jittered_points = TRUE, quantile_lines = TRUE, scale = 0.9, alpha = 0.7,
 #    vline_size = 1, vline_color = "red",
 #    point_size = 0.4, point_alpha = 1,
 #    position = position_raincloud(adjust_vlines = TRUE)
 #  )
  labs(x = "No. of individuals", y= "")+
  #geom_jitter(alpha = .1, width = 0.1, height = 0.1)+
  theme_few()

ggsave(plot = dempred, "../visuals/dempred.png", height = 8, width = 14, scale = 1.1)

@@

```{r}
mdata <- data%>%
  ungroup()%>%
  mutate(ageinyears = as.numeric(scale(ageinyears)),
         targetcentralityx = as.numeric(scale(targetcentralityx)),
         click = abs(clickdistfromtargetcenterx))

#write_csv(mdata,"../data/mdata.csv")
```

```{r}
# bm_null <- brm(click ~ ageinyears + targetcentralityx + (targetcentralityx|subjid),
#                               data   = mdata,
#                               family = lognormal(),
#                               warmup = 2000,
#                               iter   = 6000,
#                               chains = 4,
#                               cores  = 4,
#                               threads = threading(8),
#              control = list(adapt_delta = 0.95),
#              backend = "cmdstanr")
# 
# saveRDS(bm_null, "../saves/bm_cv_null.rds")
# 
# 
# bm_cult <- brm(click ~ ageinyears + targetcentralityx + (targetcentralityx|subjid)+ (targetcentralityx |community),
#                               data   = mdata,
#                               family = lognormal(),
#                               warmup = 2000,
#                               iter   = 6000,
#                               chains = 4,
#                               cores  = 4,
#                               threads = threading(8),
#              control = list(adapt_delta = 0.95),
#              backend = "cmdstanr")
# 
# saveRDS(bm_cult, "../saves/bm_cv_cult.rds")
# 
# bm_cult_age <- brm(click ~ ageinyears + targetcentralityx + (targetcentralityx|subjid)+ (ageinyears + targetcentralityx |community),
#                               data   = mdata,
#                               family = lognormal(),
#                               warmup = 2000,
#                               iter   = 6000,
#                               chains = 4,
#                               cores  = 4,
#                               threads = threading(8),
#              control = list(adapt_delta = 0.95),
#              backend = "cmdstanr")
# 
# saveRDS(bm_cult_age, "../saves/bm_cv_cult_age.rds")
# 
# fixef(bm_cult_age)%>%as_tibble(rownames = "term")%>%mutate_if(is.numeric, round, 2)%>%saveRDS(.,"../saves/cult_age_fix.rds")

@@

```{r}
# script for cross validation can be found in  `../scripts/cross_validation.R`
# cross validation is run in script `../scripts/run_cross_validation.R`, here we only load the saved output
cv_cult <- readRDS("../saves/cross_validation_result.rds")
```

@@

This prediction is best understood by considering a similar phenomenon: pointing a torch light to a flat surface. The width of the light beam represents each individual's level of uncertainty in vector estimation and is represented in the model as a normal distribution around the true gaze vector with a participant specific standard deviation. On each trial, the model assumes that the participant samples a vector from this distribution to infer the location of the balloon. The smaller the standard deviation -- -- the narrower the light beam --, the more precise on average the participant is. Now, when the torch is directed straight down, the light beam is concentrated in a relatively small area. When the torch is rotated to the side, the the light from one half of the cone must travel further than the light from the other half to reach the surface. As a consequence, the light is spread over a wider area. This is true no matter how wide the cone (how large the standard deviation) is. A formal definition of the model can be found below.

```{r}
# draws <- bind_rows(
# as_draws_df(bm_cult_age)%>%
#   select(contains("ageinyears"))%>%
#   select(contains("ageinyears"))%>%
#   select(-contains("sd"))%>%
#   select(-contains("cor"))%>%
#   pivot_longer(cols = contains("ageinyears]"), names_to = "community", values_to = "value")%>%
#   mutate(post = value + b_ageinyears,
#          community = str_remove(community, "r_community"),
#          community = str_remove(community, ",ageinyears]"),
#          community = str_remove(community, "\\["))%>%
#   select(community, post)%>%
#   mutate(type = "ageinyears"),
# 
# as_draws_df(bm_cult_age)%>%
#   select(contains("targetcentralityx"))%>%
#   select(contains("targetcentralityx"))%>%
#   select(-contains("sd"))%>%
#   select(-contains("cor"))%>%
#   select(-contains("subjid"))%>%
#   pivot_longer(cols = contains("targetcentralityx]"), names_to = "community", values_to = "value")%>%
#   mutate(post = value + b_targetcentralityx,
#          community = str_remove(community, "r_community"),
#          community = str_remove(community, ",targetcentralityx]"),
#          community = str_remove(community, "\\["))%>%
#   select(community, post)%>%
#   mutate(type = "targetcentrality")
# )%>%
#   mutate(community = str_replace(community, "\\.", " "),
#          community= str_remove(community,"\\."))
# 
# pdraws <- draws%>%
#   mutate(community = recode(community,
#                             "Auckland (NewZealand)" = "Auckland (New Zealand)",
#                             "BaYaka (Rep.Congo)" = "BaYaka (Rep. Congo)",
#                             "Bandongo (Rep.Congo)" = "Bandongo (Rep. Congo)",
#                             "Buenos Aires(Argentina)" = "Buenos Aires (Argentina)"))%>%
#   left_join(data%>%distinct(community, continent))%>%
#   mutate(continent = factor(continent, levels = c("America", "Africa", "Europe", "Asia", "Oceania"), ordered = T))
# 
# saveRDS(pdraws, "../saves/pdraws.rds")
# 
# post_agg <- pdraws%>%
#   group_by(community, type)%>%
#   summarise(mean = mean(post),
#             lci = hdi_lower(post),
#             uci = hdi_upper(post))
# 
# saveRDS(post_agg, "../saves/post_agg.rds")
```

@@

```{r}
fixef_cult_age <- readRDS("../saves/cult_age_fix.rds")
```

To test these predictions, we inspected the parameter estimates for age and target centrality in the "winning" `culture_age` model described in the previous sections. We found strong main effects of age ($\beta$ = `r fixef_cult_age%>%filter(term == "ageinyears")%>%pull(Estimate)`, SE = `r fixef_cult_age%>%filter(term == "ageinyears")%>%pull(Est.Error)`, 95% CrI = `r fixef_cult_age%>%filter(term == "ageinyears")%>%pull(Q2.5)` - `r fixef_cult_age%>%filter(term == "ageinyears")%>%pull(Q97.5)`) and target centrality ($\beta$ =`r fixef_cult_age%>%filter(term == "targetcentralityx")%>%pull(Estimate)`, SE = `r fixef_cult_age%>%filter(term == "targetcentralityx")%>%pull(Est.Error)`, 95% CrI = `r fixef_cult_age%>%filter(term == "targetcentralityx")%>%pull(Q2.5)` - `r fixef_cult_age%>%filter(term == "targetcentralityx")%>%pull(Q97.5)`). Figure \@ref(fig:figpreds) visualizes the posterior distributions for each cultural setting and shows that -- despite variation in strength -- there was a substantial effect of age and target centrality in all cultural settings.

Another way to look at these signatures is to visualize the group-level developmental trajectories and the aggregated performance at different areas of the screen. Figure \@ref(fig:figdev)A shows that children got more precise with age in all cultural settings. Figure \@ref(fig:figdev)B shows the u-shaped pattern predicted by the cognitive model: the closer the balloon lands to the center of the screen (bins 5 and 6) the more precise children are in all cultural settings.

@@

```{r}
am <- ggplot()+
  geom_point(data = devdata%>%filter(continent == "America"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
  geom_smooth(data = post%>%filter(continent == "America"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
  theme_few()+
  scale_fill_colorblind(name = "")+
  scale_color_colorblind(name = "")+
  labs(x = "", y="Imprecision")+
  scale_x_continuous(limits = c(2,10))+
  scale_y_continuous(limits = c(0,1000))+
  facet_grid(continent~.)+
  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))

af <- ggplot()+
  geom_point(data = devdata%>%filter(continent == "Africa"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
  geom_smooth(data = post%>%filter(continent == "Africa"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
  theme_few()+
  scale_fill_colorblind(name = "")+
  scale_color_colorblind(name = "")+
  labs(x = "", y="")+
    scale_x_continuous(limits = c(2,10))+
  scale_y_continuous(limits = c(0,1000))+
  facet_grid(continent~.)+
  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))

eu <- ggplot()+
  geom_point(data = devdata%>%filter(continent == "Europe"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
  geom_smooth(data = post%>%filter(continent == "Europe"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
  theme_few()+
  scale_fill_colorblind(name = "")+
  scale_color_colorblind(name = "")+
  labs(x = "", y="")+
    scale_x_continuous(limits = c(2,10))+
  scale_y_continuous(limits = c(0,1000))+
  facet_grid(continent~.)+
  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))

as <- ggplot()+
  geom_point(data = devdata%>%filter(continent == "Asia"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
  geom_smooth(data = post%>%filter(continent == "Asia"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
  theme_few()+
  scale_fill_colorblind(name = "")+
  scale_color_colorblind(name = "")+
  labs(x = "", y="")+
    scale_x_continuous(limits = c(2,10))+
  scale_y_continuous(limits = c(0,1000))+
  facet_grid(continent~.)+
  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))

oc <- ggplot()+
  geom_point(data = devdata%>%filter(continent == "Oceania"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
  geom_smooth(data = post%>%filter(continent == "Oceania"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
  theme_few()+
  scale_fill_colorblind(name = "")+
  scale_color_colorblind(name = "")+
  labs(x = "Age", y="")+
    scale_x_continuous(limits = c(2,10))+
  scale_y_continuous(limits = c(0,1000))+
  facet_grid(continent~.)+
  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
```

@@

Table \@ref(tab:bftable) shows the Bayes Factors in favor of the vector-based gaze estimation model for each cultural setting. The evidence in favor of the gaze model compared to the two alternative models was clear (all BF > 1 000 000 000 000 000). This result rules out that the u-shaped pattern in the data was the result of participants always clicking the center instead of following gaze.

```{r bftable, echo=F}
bf <- readRDS("../model/output/bf_comparison.rds")%>%
  mutate_if(is.numeric, format, digits = 2, nsmall = 2)%>%
  mutate(community = recode(community,
                            nigeria = "Akure (Nigeria)",
                            leipzig = "Leipzig (Germany)",
                            `hai||om` = "Hai||om (Namibia)",
                            khwe = "Khwe (Namibia)",
                            windhoek = "Windhoek (Namibia)",
                            stanford = "Stanford (USA)",
                            chimfunshi = "Chimfunshi (Zambia)",
                            mexico = "Ocuilan (Mexico)",
                            plymouth = "Plymouth (UK)",
                            china = "Beijing (China)", 
                            india = "Pune (India)",
                            argentina = "Buenos Aires (Argentina)",
                            auckland = "Auckland (New Zealand)",
                            turkey = "Malatya (Türkiye)",
                            bandongo = "Bandongo (Rep. Congo)",
                            bayaka = "BaYaka (Rep. Congo)", 
                            uganda = "Nyabyeya (Uganda)"))

@@

We asked about children's exposure to screens as well as touchscreens. These two variables were largely redundant (see Figure \@ref(fig:figpred1)B) and so we included only one of them in the model. We chose the availability of a touchscreen as a predictor because the task itself was presented on a touchscreen. We expected (and pre-registered) that children with exposure to touchscreens would perform better.

For household composition, we asked for the total number of people in the household, the number of children and the number of younger children. We standardized each predictor *within* each culture before fitting the models. Thus, the interpretation of the coefficient is the gain in precision for living e.g., in a larger household relative to other children from the same cultural settings.

@@

ggsave(plot = pcomtc, "../visuals/pcomtc.png", height = 4, width = 5, scale = 1.5)

knitr::include_graphics("../visuals/pcomtc.png")
```
